---
title: "README-statemaps"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# statemaps
Perform basic functions for basic map function, including 51 states and DC. Basic functions include
 clipper to create an outside mask to cover unwanted area for state or county maps
 mapscale to add scale bar to an existing map
 northarrow to add north arrow 
 colbar to add county map and scaled color bar to the right.

Installation
-----------------
'# Installing just this library (should get all dependancies)
library(devtools) 
install.git_hub("kevinlzheng/statemaps")

'# Installing dependancies separately
'# set CRAN mirror 
'#(loads gui in R; in R-Studio select ## of mirror in Console pane)
'# If know mirror can use "ind=" in 2nd statement and comment out (prefix line with #) the first.
chooseCRANmirror()
'#chooseCRANmirror(ind=21)
'################################################
'# must run "chooseCRANmirror()" by itself before running the rest of the script

'# libraries to be installed
data.packages = c(                  
                  "devtools"        # install helper for non CRAN libraries
                  ,"installr"       # install helper
                  ,"digest"         # caused error in R v3.2.3 without it
                  ,"dataRetrieval"  # loads USGS data into R
                  ,"knitr"          # create documents in other formats (e.g., PDF or Word)
                  ,"htmltools"      # needed for knitr and doesn't always install properly with Pandoc
                  ,"rmarkdown"      # needed for knitr and doesn't always install properly with Pandoc
                  ,"htmltools"      # a dependency that is sometimes missed.
                  ,"evaluate"       # a dependency that is sometimes missed.
                  ,"highr"          # a dependency that is sometimes missed.
                  ,"rmarkdown"      # a dependency that is sometimes missed.
                  ,"RColorBrewer"   # for coloring boxplot 
                  ,"crayon"
                  ,"rprojroot"
                  ,"rdal"
                  ,"sp"
                  )
                  
lapply(data.packages,function(x) install.packages(x))

'## pandoc
require(installr)
install.pandoc()


Purpose
--------------
The scatter plot and multiple regression functions have been used for a long time for various projects. 

Usage
------------




